Personalization and probabilities: impersonal propensities in online grocery shopping

### 2017-10-05 reply_to_reviews.md

Dear Evelyn
This is the re-written version of my earlier submission. I've pasting my response to the reviews below.

best wishes

Adrian Mackenzie

-----------------------------

@@

Thanks very much to reviewers for their work on what must have seemed like a frustrating and elusive manuscript. The reviews have been a great help in re-writing the piece. The reviews were quite long, so I won't summarise all the changes I've made in response. There were many. The main focus in the re-writing of the manuscript was the overall argument.

Much of the call for clarification concerned the main argument. It has too many  threads. It was engaging in several different debates at once -- about recommender systems and their exploitative effects on  consumption practices, about recommender systems as examples of how big data practices take root in specific sectors, and recommender systems as symptom of some kind of more ontological transformation in sociotechnical collectives.  In the re-write, I've mainly sought to clarify the argument: grocery recommender systems are a mundane example of changes associated with big data; personalization is a powerful ordering technique in big data practice; but personalization cannot account for either the range of practices associated with big data or the broader associated transformations.  The case of  'conversion' of the Tesco grocery recommender system to a personal relevancy model helps make this argument: grocery shopping is a complex social negotiation, intimately entwined with social groups (family, household, etc). Data-mining to target grocery shoppers pre-dates by several decades recent growth in predictive analytics. A personalized recommender system, based even on post-demographic data, will struggle to effectively personalize grocery recommendations.

The manuscript has been rewritten from almost the ground up. It would be hard to list all the changes. Many of them respond to specific points in the reviews relating to relevant literature or problems in argumentation.   The basic idea of the rewrite was remove any thread of discussion that didn't relate to the main argument. A lot of the discussion of list practice and orderings was distracting so that has been reduced to a minimum. I wasn't able to provide the more substantial empirical engagement requested by Reviewer 2. That would entail a new research project.  The case study cannot make any claims to ethnographic thickness, so what the paper does to deepen its argumentative engagement around personalization in order to develop a more genealogical account based  on  research literature, widely used software and some examples of data from the Tesco API.

Main points from reviews:

### 2017-10-05 log.rmd
submitting rewritten version

>>>>

## Thu 05 Oct 2017 11:59:08 BST
- submitting it as a new submission. The old one was BDS-17-0018. Does that mean that by march there were 18 submissions?   
- reconstruction.docx is the main file. It has been handtweaked in various ways, but most of these have been put back into reconstruction.rmd.
- figure numbering is still not right. Done that by hand.

### 2017-10-05 reconstruction.rmd
submitting rewritten version

```{r arules-ex, cache=TRUE, fig.cap='Frequency of association betwene items in the `Grocery` dataset', message=FALSE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
```

@@

```{r arules-ex2}
options(digits=2)
rules<- apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=FALSE))
rules_sorted <- sort(rules, decreasing=TRUE,by="confidence")
kable(inspect(rules_sorted[1:5]), caption='The first five association rules for the `Groceries` dataset')
```

@@

```{r tesco-ex, echo=FALSE, cache=TRUE, fig.cap ='Tesco surplus',  fig.margin=TRUE}
    library(ggplot2)
    tesco = read.csv('data/reference_data/tesco_groceries.csv')
    total = sum(tesco$actual, na.rm=TRUE)
    tesco = na.omit(tesco)
    tesco$actual = as.integer(tesco$actual)
    ggplot(tesco[tesco$actual>50,],
        aes(x=labels, y=actual, fill=labels)) +
        geom_bar(stat='identity') + coord_flip() +
        ggtitle('Tesco grocery items with more than 50 products') +
        theme(legend.position="none", axis.text=element_text(size=7))

```

>>>>

```{r arules-ex, cache=TRUE, fig.cap='Frequency of items in the `Grocery` dataset', message=FALSE, echo=FALSE, fig.margin=TRUE}
library(knitr)
library(arules)
library(arulesViz)
library(datasets)
data(Groceries)
itemFrequencyPlot(Groceries,topN=10,col=rainbow(10), ntype="absolute",  cex.axis = 0.55)
```

@@

```{r arules-ex2, echo=FALSE}
options(digits=2)
rules<- apriori(data=Groceries, parameter=list(supp=0.001,conf = 0.15,minlen=2), appearance = list(default="rhs",lhs="whole milk"), control = list(verbose=FALSE))
rules_sorted <- sort(rules, decreasing=TRUE,by="confidence")
kable(inspect(rules_sorted[1:5]), caption='The first five association rules for the `Groceries` dataset')
```

@@

```{r tesco-ex, echo=FALSE, cache=TRUE, fig.cap ='Tesco grocery items with more than 50 products',  fig.margin=TRUE}
    library(ggplot2)
    tesco = read.csv('data/reference_data/tesco_groceries.csv')
    total = sum(tesco$actual, na.rm=TRUE)
    tesco = na.omit(tesco)
    tesco$actual = as.integer(tesco$actual)
    ggplot(tesco[tesco$actual>50,],
        aes(x=labels, y=actual, fill=labels)) +
        xlab('Item count') + ylab('Grocery item') +
        geom_bar(stat='identity') + coord_flip() +
        theme(legend.position="none", axis.text=element_text(size=7))

ggsave('figure/tesco_grocery_lines.svg')
ggsave('figure/tesco_grocery_lines.png')
```
